Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2019-01-24 RNARedPrint.tex
fig3 caption clearer

%To reduce the cost of the precomputation, we used a stacking energy model
%as a proxy for the Turner model. Indeed, we observed a strong linear
%dependency between the Turner energy and the
%emphasize that only the simple stacking energies are directly targeted
%(at $\pm$10\% tolerance, except for a few hard instances). Due to our
%linear adjustment, we finally achieve well-controlled energies in the
%realistic Turner energy model.
\begin{figure*}[t]
  \begin{center}
    %{\sf \bfseries A}\
    \includegraphicstop[width=0.97\textwidth]{Figs/energy_shift}\hfill
    %{\sf \bfseries B}\ \includegraphicstop[width=0.55\textwidth]{Figs/PKB00211_PKB00239_0_energy_distribution}
  \end{center}
  \caption{%
    Targeting specific energies for pseudoknotted structures using
    multi-dimensional Boltzmann sampling. \textbf{(A)} Linear fits between the
    energies in the stacking model to the realistic pseudoknot energy
    model by Dirks and Pierce (D\&P) for the sampled sequences and both target structures R1 and R2. The good
    match \revised{(respective $R^2$ values of $0.846$ and $0.841$)} enables more efficient targeting of Turner energies based on
    targeting stacking model energies.  We show the fits for both
    target structures R1 and R2 of subfigure B.  \textbf{(B)} D\&P energy
    distributions for two target structures R1 and R2. We show the
    results of targeting the respective free energies $(-30,-20)$,
    $(-30,-30)$, $(-25,-25)$, and $(-20,-30)$ for the target
    structures---this demonstrates the effectivity of our adaptive
    multi-dimensional Boltzmann sampling procedure; moreover, for
    comparison, the distributions for uniform and Boltzmann
    samples---respectively associated with homogenous weights $1$ and
    $e^\beta$.
%    ($\delta=0.05, \delta'=0.1, \gamma=1.1, \psi=20, n=1000$)
  }
  \label{fig:energydist-pk}
\end{figure*}

>>>>

%To reduce the cost of the precomputation, we used a stacking energy model
%as a proxy for the Turner model. Indeed, we observed a strong linear
%dependency between the Turner energy and the
%emphasize that only the simple stacking energies are directly targeted
%(at $\pm$10\% tolerance, except for a few hard instances). Due to our
%linear adjustment, we finally achieve well-controlled energies in the
%realistic Turner energy model.
\begin{figure*}[t]
  \begin{center}
    %{\sf \bfseries A}\
    \includegraphicstop[width=0.97\textwidth]{Figs/energy_shift}\hfill
    %{\sf \bfseries B}\ \includegraphicstop[width=0.55\textwidth]{Figs/PKB00211_PKB00239_0_energy_distribution}
  \end{center}
  \caption{%
    Targeting specific energies for pseudoknotted structures using
    multi-dimensional Boltzmann sampling. \textbf{(A)} Linear fits between the
    energies in the stacking model to the realistic pseudoknot energy
    model by Dirks and Pierce (D\&P) for \revised{initially} sampled sequences and both target structures R1 and R2 (shown in subfigure B). The good
    match \revised{(respective $R^2$ values of $0.846$ and $0.841$)} enables more efficient targeting of Turner energies based on
    targeting stacking model energies. \textbf{(B)} Resulting D\&P energy distributions for the two target structures R1 and R2 when aiming for the respective free energies $(-30,-20)$,
    $(-30,-30)$, $(-25,-25)$, and $(-20,-30)$. These demonstrate the effectivity of our adaptive
    multi-dimensional Boltzmann sampling procedure, especially by comparing the distributions to those of uniform and Boltzmann sampled sequences, with homogenous weights $1$ and
    $e^\beta$, respectively.
%    ($\delta=0.05, \delta'=0.1, \gamma=1.1, \psi=20, n=1000$)
  }
  \label{fig:energydist-pk}
\end{figure*}
